---
output:
  md_document:
    variant: markdown_github
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 4)
library(tidyverse)
load("data/processed.RData")
load("data/features.RData")
```
# Discovery's Search Engine Comparison

Comparison of zero results rate for query features across search engines ([T136377](https://phabricator.wikimedia.org/T136377)). The idea is to take a sample of queries exhibiting particular features (and/or combinations of features) and then compare our ZRR with Google's/Bing's/site:wikipedia.org/etc. to see which high-ZRR features on our side have significantly lower ZRR on other search engines. This could highlight certain query categories for us and help us prioritize our work on improving ZRR.

## Setup

### R Packages

```R
install.packages(c("devtools", "magrittr", "tidyverse", "import", "httr", "urltools", "rvest", "binom"))
```

### Hive

The stratified sampling employs [a custom ranking UDF](hive/RankUDF.java) and UDFs from [Wikimedia Analytics' Refinery](https://github.com/wikimedia/analytics-refinery-source).

## Data

1. First, [a shell script](hive/script.sh) runs [this Hive query](hive/extract_queries.hql), which returns at most N=100 random queries for each combination of [query features](https://github.com/wikimedia/analytics-refinery-source/blob/master/refinery-core/src/main/java/org/wikimedia/analytics/refinery/core/SearchQuery.java)
2. Those queries are [processed in R](fetch_queries.R) and are manually checked for presence of PII
3. The processed queries are [automatically run through](process_queries.R) major [search engines](search_engines.R)
4. We also calculate the % of total queries that each combination of features represents by [counting queries by features](hive/count_features.hql)
5. Then we calculate each combination's zero results rate from each engine

## Results

The bots encountered problems performing some searches, so the table below is incomplete, but should provide a good starting point for discussion. Not all queries were successfully searched for, so we include the fraction of zero result SERPs out of successfully searched queries on a per-engine basis. The "Proportion" column represents the % of full-text searches performed on EnWiki by U.S.-based website visitors on desktops in September and October of 2016.

```{r zero_results, results = 'asis'}
zero_results <- queries %>%
  group_by(features) %>%
  summarize(cirrus_n = n(),
            cirrus_zr = sum(zero_result_enwiki, na.rm = TRUE),
            google_n = sum(!is.na(zero_results_google)),
            google_zr = sum(zero_results_google, na.rm = TRUE),
            enwiki_via_google_n = sum(!is.na(zero_results_enwiki_via_google)),
            enwiki_via_google_zr = sum(zero_results_enwiki_via_google, na.rm = TRUE),
            yahoo_n = sum(!is.na(zero_results_yahoo)),
            yahoo_zr = sum(zero_results_yahoo, na.rm = TRUE),
            bing_n = sum(!is.na(zero_results_bing)),
            bing_zr = sum(zero_results_bing, na.rm = TRUE),
            ddg_n = sum(!is.na(zero_results_ddg)),
            ddg_zr = sum(zero_results_ddg, na.rm = TRUE)) %>%
  ungroup %>%
  mutate(
    google_zr = ifelse(google_n == 0, NA, google_zr),
    enwiki_via_google_zr = ifelse(enwiki_via_google_n == 0, NA, enwiki_via_google_zr),
    yahoo_zr = ifelse(yahoo_n == 0, NA, yahoo_zr),
    bing_zr = ifelse(bing_n == 0, NA, bing_zr),
    ddg_zr = ifelse(ddg_n == 0, NA, ddg_zr)
  ) %>%
  left_join(features[, c("features", "proportion_total", "proportion_interested")], by = "features")

zero_results %>%
  arrange(desc(proportion_total)) %>%
  transmute(
    `Features` = features,
    `Proportion` = sprintf("%.6f%%", 100 * proportion_total),
    `Cirrus ZRR` = sprintf("%.0f%% (%.0f/%.0f)", 100 * cirrus_zr/cirrus_n, cirrus_zr, cirrus_n),
    `Google ZRR` = sprintf("%.0f%% (%.0f/%.0f)", 100 * google_zr/google_n, google_zr, google_n),
    # `Google +site:enwiki ZRR` = sprintf("%.0f%% (%.0f/%.0f)", 100 * enwiki_via_google_zr/enwiki_via_google_n, enwiki_via_google_zr, enwiki_via_google_n),
    `Yahoo ZRR` = sprintf("%.0f%% (%.0f/%.0f)", 100 * yahoo_zr/yahoo_n, yahoo_zr, yahoo_n),
    `Bing ZRR` = sprintf("%.0f%% (%.0f/%.0f)", 100 * bing_zr/bing_n, bing_zr, bing_n),
    `DDG ZRR` = sprintf("%.0f%% (%.0f/%.0f)", 100 * ddg_zr/ddg_n, ddg_zr, ddg_n)
  ) %>%
  knitr::kable(format = "markdown", align = c("l", "r", rep("r", 6))) %>%
  gsub("NA% (NA/0)", "", ., fixed = TRUE)
```
